---
title: "GSE28644 Analysis"
author: "David Cooper"
date: "2022-09-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(GEOquery)
library(limma)
library("affycoretools")
library(affy)
library(tidyverse)
library(fgsea)
library(data.table)
library(preprocessCore)
library(pheatmap)
library(biomaRt)
source("read_cpdb_tab.R")

```

## Data Acquisition

Use GEOquery to obtain the GEO series GSE28644. GSEMatrix=FALSE will pull out all the sample information as a GSE object. GSEMatrix=TRUE is the default and will provide a list of expression sets. Can use [[1]] to pull out the GSE object if there is only one. exprs() will return just the expression data and can be used to log transform the data if desired. 
https://bioconductor.org/packages/release/bioc/vignettes/GEOquery/inst/doc/GEOquery.html

```{r Get ExpressionSets}
set.seed(123)
GSEname="GSE28644"
GSE=getGEO(GSEname)
exGSE=GSE[[1]]
exprs(exGSE)=log2(exprs(exGSE))
SampleData=read.table("GSE28644_sample_data.txt",header = TRUE,sep = "\t")
pData(exGSE)$response=SampleData$response

```

## Quality Control Analyses 

Compare samples with boxplots and PCA to assess the quality across samples. Normalized datasets should have the same median across the samples. The boxplot will show if there are any samples that differ from the rest. 

```{r Boxplots}
#Boxplot with all samples, log 2 transformed
boxplot(exprs(exGSE),las=2)
#Quantile plot with all samples
qs=t(apply(exprs(exGSE),2,quantile,prob=c(0.05,0.25,0.5,0.75,0.95)))
matplot(qs,type="l",lty=1)

```

Principal component analysis (PCA). plotPCA(outside=TRUE) will place the legend on the outside of the plot.

```{r PCA}
#Characteristics to group by
#colnames(exGSE@phenoData@data)
#Samples all individual
plotPCA(exGSE,outside=TRUE)
#Samples grouped by Treatment
plotPCA(exGSE, groups = as.numeric(as.factor(exGSE@phenoData@data$source_name_ch1)), groupnames = gsub(".*group ","",levels(as.factor(exGSE@phenoData@data$source_name_ch1))),outside=TRUE)
#Samples grouped by Strain
plotPCA(exGSE, groups = as.numeric(as.factor(exGSE@phenoData@data$characteristics_ch1)), groupnames = gsub("strain: ","",levels(as.factor(exGSE@phenoData@data$characteristics_ch1))),outside=TRUE)
#Samples grouped by Response
plotPCA(exGSE, groups = as.numeric(as.factor(exGSE@phenoData@data$response)), groupnames = gsub("strain: ","",levels(as.factor(exGSE@phenoData@data$response))),outside=TRUE)


```

## Remove Low-expressed genes

Removal of gene loci without expression above a threshold in at least half of the samples. First check what the lowest expression is for each sample. If no sample has any low expression levels, no filtering is done. 

```{r}
for(i in 1:as.numeric(ncol(exGSE))){print(min(exprs(exGSE[,i])))}
fexGSE=exGSE
ZeroCounts=as.numeric()
for(i in 1:as.numeric(nrow(exGSE))){
  ZeroCounts[i]=sum(exprs(exGSE)[i,]<2.1)
  }
hist(ZeroCounts)
fexGSE@featureData@data$ZeroCounts=ZeroCounts
fexGSE@featureData@varMetadata[17,]=c("ZeroCount","number of samples with zero counts",NA)
fexGSE=fexGSE[fexGSE@featureData@data$ZeroCounts<30,]

```

## Differential Expression Analysis

Use limma to analyze expression treatment vs. control with paired patient samples (section 9.4.1). >limmaUsersGuide() to open the users guide manual.

```{r Paired Patient Samples Analysis}
#Analysis using log2 transformed data
#All samples
#Define variables for model matrix
Treatment=as.factor(fexGSE@phenoData@data$source_name_ch1)
Strain=as.factor(fexGSE@phenoData@data$characteristics_ch1)
Names=fexGSE@phenoData@data$geo_accession
#Design matrix
Design=model.matrix(~Treatment+Strain)
rownames(Design)=Names
#DE analysis
fit=lmFit(fexGSE,Design)
fit2=eBayes(fit)
colnames(fit2) #To identify coef name to use in topTable
topTable(fit2,coef = "Treatmenttreatment group (fluoxetine)")
saveRDS(fit2,"../FLX_datasets/GSE28644/DE_GSE28644.rds")

#Responders
#Define variables for model matrix
fexResponders=fexGSE[,rownames(na.omit(fexGSE@phenoData@data[fexGSE@phenoData@data$response=="positive",]))]
rTreatment=as.factor(fexResponders@phenoData@data$source_name_ch1)
rStrain=as.factor(fexResponders@phenoData@data$characteristics_ch1)
rNames=fexResponders@phenoData@data$geo_accession
#Design matrix
rDesignPair=model.matrix(~rTreatment+rStrain)
rownames(rDesignPair)=rNames
#DE analysis
rpairfit=lmFit(fexResponders,rDesignPair)
rpairfit2=eBayes(rpairfit)
colnames(rpairfit2)
topTable(rpairfit2,coef = "rTreatmenttreatment group (fluoxetine)")
saveRDS(rpairfit2,"../FLX_datasets/GSE28644/DE_Res_GSE28644.rds")

#Nonresponders
#Define variables for model matrix
fexNon=fexGSE[,rownames(na.omit(fexGSE@phenoData@data[fexGSE@phenoData@data$response=="negative",]))]
nTreatment=as.factor(fexNon@phenoData@data$source_name_ch1)
nStrain=as.factor(fexNon@phenoData@data$characteristics_ch1)
nNames=fexNon@phenoData@data$geo_accession
#Design matrix
nDesignPair=model.matrix(~nTreatment+nStrain)
rownames(nDesignPair)=nNames
#DE analysis
npairfit=lmFit(fexNon,nDesignPair)
npairfit2=eBayes(npairfit)
colnames(npairfit2)
topTable(npairfit2,coef = "nTreatmenttreatment group (fluoxetine)")
saveRDS(npairfit2,"../FLX_datasets/GSE28644/DE_Non_GSE28644.rds")

#Responders vs Nonresponders
#Define variables for model matrix
fexRandN=fexGSE[,rownames(na.omit(fexGSE@phenoData@data[fexGSE@phenoData@data$response=="negative"|fexGSE@phenoData@data$response=="positive",]))]
TreatResponse=factor(paste(fexRandN@phenoData@data$source_name_ch1,fexRandN@phenoData@data$response,sep="_"))
vNames=fexRandN@phenoData@data$geo_accession
#Design matrix
DesignResponse=model.matrix(~0+TreatResponse)
rownames(DesignResponse)=vNames
colnames(DesignResponse)=c("CNR","CR","FNR","FR")
#DE analysis
Responsefit=lmFit(fexRandN, DesignResponse)
contrasts_Response=makeContrasts(FR - FNR, FR - CR, FNR - CNR, CR - CNR, levels = DesignResponse)  
Responsefit2=contrasts.fit(Responsefit,contrasts_Response)
Responsefit2=eBayes(Responsefit2)
topTable(Responsefit2,coef = "FR - FNR")
saveRDS(Responsefit2,"../FLX_datasets/GSE28644/DE_ResVNon_GSE28644.rds")


```

## Differential Expression Plots

Volcano plots for fit2 DE tables. Scatter plot stats for subsets of data in a merged table

```{r Volcano Plots}
volcanoplot(fit2,coef = "Treatmenttreatment group (fluoxetine)",main="Fluoxetine vs. Control")

volcanoplot(Responsefit2,coef="FR - FNR")
```

## Gene Set Enrichment Analysis

Use fgsea to analyze gene set enrichment.

```{r Remove Duplicate Genes}
#Get the average expression across all samples for each locus
UniqueGenes=data.frame(AVG_EXPR=rowMeans(exprs(fexGSE)),
                       LOCI=fexGSE@featureData@data$ID,
                       GENE_SYMBOL=fexGSE@featureData@data$`Gene Symbol`,
                       ENTREZ_ID=fexGSE@featureData@data$ENTREZ_GENE_ID) %>%
  arrange(desc(AVG_EXPR)) %>%
  filter(!duplicated(ENTREZ_ID)) %>%
  filter(ENTREZ_ID!="")
#Get ensembl gene IDs using biomart
ensembl=useEnsembl(biomart="genes",dataset = "mmusculus_gene_ensembl")
attributes = listAttributes(ensembl)
MouseGeneList=getBM(mart = ensembl,attributes = c("entrezgene_id","ensembl_gene_id"))
UniqueGenes$ENSEMBL_GENE=MouseGeneList$ensembl_gene_id[match(UniqueGenes$ENTREZ_ID,MouseGeneList$entrezgene_id)]
UniqueGenes=filter(UniqueGenes,ENSEMBL_GENE!="")%>%filter(!duplicated(ENSEMBL_GENE))

```

    GSE28644_Cortex_XFTUXX
    GSE28644_Cortex_XFRNXX
    GSE28644_Cortex_XFRCXX
    GSE28644_Cortex_XFNCXX
    
```{r GSEA using fgsea}
#Pathways list using mouse ensembl gene symbol (Mouse)
CPDBpaths=read_cpdb_tab("CPDB_pathways_genes_mouse.tab")

DElist=list()

#Pooled treatment vs control (t stat and gene symbols) using filtered genes list
PooledFilter=topTable(fit2,coef = "Treatmenttreatment group (fluoxetine)",number = Inf)%>%filter(ID%in%UniqueGenes$LOCI)
PooledFilter$GENE_SYMBOL=UniqueGenes$ENSEMBL_GENE[match(PooledFilter$ID,UniqueGenes$LOCI)]
DElist$XFTU=PooledFilter[PooledFilter$P.Value<0.05,]$Gene.Symbol
DEbackground=PooledFilter$Gene.Symbol
tstats=PooledFilter$t
names(tstats)=PooledFilter$GENE_SYMBOL
GeneEnrich=fgsea(pathways = CPDBpaths, stats = tstats, minSize  = 10, nPermSimple=10000)
saveRDS(GeneEnrich,"../FLX_datasets/GSE28644/GSEA_Pooled_GSE28644.rds")

#Stats vector for responders, patient-pairs treatment vs control (t stat and gene symbols) using filtered genes list
RespondersFilter=topTable(rpairfit2,coef = "rTreatmenttreatment group (fluoxetine)",number = Inf)%>%filter(ID%in%UniqueGenes$LOCI)
RespondersFilter$GENE_SYMBOL=UniqueGenes$ENSEMBL_GENE[match(RespondersFilter$ID,UniqueGenes$LOCI)]
DElist$XFRC=RespondersFilter[RespondersFilter$P.Value<0.05,]$Gene.Symbol
rtstats=RespondersFilter$t
names(rtstats)=RespondersFilter$GENE_SYMBOL
rGeneEnrich=fgsea(pathways = CPDBpaths, stats = rtstats, minSize  = 10, nPermSimple=10000)
saveRDS(rGeneEnrich,"../FLX_datasets/GSE28644/GSEA_Res_GSE28644.rds")

#Stats vector for non-responders, patient-pairs treatment vs control (t stat and gene symbols) using filtered genes list
NonFilter=topTable(npairfit2,coef = "nTreatmenttreatment group (fluoxetine)",number = Inf)%>%filter(ID%in%UniqueGenes$LOCI)
NonFilter$GENE_SYMBOL=UniqueGenes$ENSEMBL_GENE[match(NonFilter$ID,UniqueGenes$LOCI)]
DElist$XFNC=NonFilter[NonFilter$P.Value<0.05,]$Gene.Symbol
ntstats=NonFilter$t
names(ntstats)=NonFilter$GENE_SYMBOL
nGeneEnrich=fgsea(pathways = CPDBpaths, stats = ntstats, minSize  = 10, nPermSimple=10000)
saveRDS(nGeneEnrich,"../FLX_datasets/GSE28644/GSEA_Non_GSE28644.rds")

#Responders vs Non-responders
VFilter=topTable(Responsefit2,coef = "FR - FNR",number = Inf)%>%filter(ID%in%UniqueGenes$LOCI)
VFilter$GENE_SYMBOL=UniqueGenes$ENSEMBL_GENE[match(VFilter$ID,UniqueGenes$LOCI)]
DElist$XFRN=VFilter[VFilter$P.Value<0.05,]$Gene.Symbol
vtstats=VFilter$t
names(vtstats)=VFilter$GENE_SYMBOL
vGeneEnrich=fgsea(pathways = CPDBpaths, stats = vtstats, minSize  = 10, nPermSimple=10000)
saveRDS(vGeneEnrich,"../FLX_datasets/GSE28644/GSEA_ResVNon_GSE28644.rds")

#Responders vs Non-responders
XFilter=topTable(Responsefit2,coef = "CR - CNR",number = Inf)%>%filter(ID%in%UniqueGenes$LOCI)
XFilter$GENE_SYMBOL=UniqueGenes$ENSEMBL_GENE[match(XFilter$ID,UniqueGenes$LOCI)]
Xtstats=XFilter$t
names(Xtstats)=XFilter$GENE_SYMBOL
XGeneEnrich=fgsea(pathways = CPDBpaths, stats = Xtstats, minSize  = 10, nPermSimple=10000)
saveRDS(XGeneEnrich,"../FLX_datasets/GSE28644/GSEA_UnResVNon_GSE28644.rds")

write.table(t(plyr::ldply(DElist,rbind)),"../FLX_datasets/GSE28644/GSE28644-DElist.txt",sep = "\t",na = "",quote = FALSE,col.names = FALSE,row.names = FALSE)
write.table(DEbackground,"../FLX_datasets/GSE28644/GSE28644-DEbackground.txt",quote = FALSE,col.names = FALSE,row.names = FALSE)


```

```{r Heatmaps GSEA}
#specify gene list from select path in CPDBpaths
TargetGenes=CPDBpaths[["Cholesterol biosynthesis | Reactome"]]
#Select expression data from subset of samples for corresponding genes
Exprs=as.data.frame(exprs(fexGSE))
Exprs=filter(Exprs,rownames(Exprs)%in%UniqueGenes$LOCI)
rownames(Exprs)=UniqueGenes$ENSEMBL_GENE[match(rownames(Exprs),UniqueGenes$LOCI)]
ExSubset=Exprs[rownames(Exprs)%in%TargetGenes,]
#Prepare annotation dataframe
ColumnNames=data.frame(Sample=gsub("Cortex_","",fexGSE@phenoData@data$title),Treatment=Treatment)
rownames(ColumnNames)=fexGSE@phenoData@data$geo_accession
#Filter out rows that all have the same value
row_sd=apply(ExSubset, 1, sd)
table(row_sd==0)
FilteredExSubset=cbind(ExSubset,sd=row_sd)%>%filter(sd!=0)%>%dplyr::select(!sd)
#Make heatmap
pheatmap(FilteredExSubset,scale = "row",annotation_col = ColumnNames)

```

