---
title: "GSE48951 Analysis"
author: "David Cooper"
date: "2022-11-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(GEOquery)
library(limma)
library("affycoretools")
library(affy)
library(tidyverse)
library(fgsea)
library(data.table)
library(preprocessCore)
library(pheatmap)
library(biomaRt)
library(stringi)
source("read_cpdb_tab.R")

```

## Data Acquisition

Use GEOquery to obtain the GEO series GSE48951. 

```{r Get ExpressionSets}
GSE=getGEO("GSE48951")
exGSE=GSE[[1]]

pData(exGSE)$RepGroup=stri_sub(exGSE$title,-5,-5)
h1exGSE=exGSE[,exGSE$`timepoint:ch1`=="1h"]
h2exGSE=exGSE[,exGSE$`timepoint:ch1`=="2h"]
h4exGSE=exGSE[,exGSE$`timepoint:ch1`=="4h"]
h8exGSE=exGSE[,exGSE$`timepoint:ch1`=="8h"]

```

## Quality Control Analyses 

Compare samples with boxplots and PCA to assess the quality across samples. 

```{r Boxplots}
#Boxplots
boxplot(exprs(exGSE),las=2)
boxplot(log2(exprs(exGSE)),las=2)
#Quantile plot with all samples
qs=t(apply(exprs(exGSE),2,quantile,prob=c(0.05,0.25,0.5,0.75,0.95)))
matplot(qs,type="l",lty=1)

```

```{r PCA All Data}
#All data
#Timepoint groups
plotPCA(exGSE, groups = as.numeric(as.factor(exGSE$`timepoint:ch1`)), groupnames = levels(as.factor(exGSE$`timepoint:ch1`)),outside=TRUE)
#Treatment groups
plotPCA(exGSE, groups = as.numeric(as.factor(exGSE$`drug:ch1`)), groupnames = levels(as.factor(exGSE$`drug:ch1`)),outside=TRUE)
#Rep groups
plotPCA(exGSE, groups = as.numeric(as.factor(exGSE$RepGroup)), groupnames = levels(as.factor(exGSE$RepGroup)),outside=TRUE)

```

```{r PCA Highlight batches}
pData(exGSE)$Index=1:ncol(exGSE)

plotPCA(exGSE, groups = as.numeric(exGSE$Index),outside=TRUE)

PCA=prcomp(t(exprs(exGSE)))
dim(PCA)
view(PCA$x)
plot(PCA$x[,1])

```

```{r PCA 1hour}
#1 hour group
#Treatment groups
plotPCA(h1exGSE, groups = as.numeric(as.factor(h1exGSE$`drug:ch1`)), groupnames = levels(as.factor(h1exGSE$`drug:ch1`)),outside=TRUE)
#Rep groups
plotPCA(h1exGSE, groups = as.numeric(as.factor(h1exGSE$RepGroup)), groupnames = levels(as.factor(h1exGSE$RepGroup)),outside=TRUE)

```

```{r PCA 2hour}
#2 hour group
#Treatment groups
plotPCA(h2exGSE, groups = as.numeric(as.factor(h2exGSE$`drug:ch1`)), groupnames = levels(as.factor(h2exGSE$`drug:ch1`)),outside=TRUE)
#Rep groups
plotPCA(h2exGSE, groups = as.numeric(as.factor(h2exGSE$RepGroup)), groupnames = levels(as.factor(h2exGSE$RepGroup)),outside=TRUE)

```

```{r PCA 4hour}
#4 hour group
#Treatment groups
plotPCA(h4exGSE, groups = as.numeric(as.factor(h4exGSE$`drug:ch1`)), groupnames = levels(as.factor(h4exGSE$`drug:ch1`)),outside=TRUE)
#Rep groups
plotPCA(h4exGSE, groups = as.numeric(as.factor(h4exGSE$RepGroup)), groupnames = levels(as.factor(h4exGSE$RepGroup)),outside=TRUE)

```

```{r PCA 8hour}
#8 hour group
#Treatment groups
plotPCA(h8exGSE, groups = as.numeric(as.factor(h8exGSE$`drug:ch1`)), groupnames = levels(as.factor(h8exGSE$`drug:ch1`)),outside=TRUE)
#Rep groups
plotPCA(h8exGSE, groups = as.numeric(as.factor(h8exGSE$RepGroup)), groupnames = levels(as.factor(h8exGSE$RepGroup)),outside=TRUE)


```

## Expression Analysis

Use limma to analyze expression to compare fluoxetine vs. control.

```{r Expression Analysis}
Names=exGSE$geo_accession
Treatment=factor(exGSE$`drug:ch1`,levels=levels(as.factor(exGSE$`drug:ch1`))[c(4,1,3,2,5)])
#Time=factor(exGSE$`timepoint:ch1`,levels = levels(as.factor(exGSE$`timepoint:ch1`)))
Design=model.matrix(~Treatment)
rownames(Design)=Names
fit=lmFit(exGSE, Design)
fit2=eBayes(fit)
topTable(fit2,coef = "TreatmentFluoxetine",number = 30)
saveRDS(fit2,"../FLX_datasets/GSE48951/DE_GSE48951.rds")

```

```{r Expression Analysis Timepoint Groups}
h1Names=h1exGSE$geo_accession
h1Treatment=factor(h1exGSE$`drug:ch1`,levels=levels(as.factor(h1exGSE$`drug:ch1`))[c(4,1,3,2,5)])
#h1RepGroup=factor(h1exGSE$RepGroup)
Designh1=model.matrix(~h1Treatment)
rownames(Designh1)=h1Names
h1fit=lmFit(h1exGSE, Designh1)
h1fit2=eBayes(h1fit)
topTable(h1fit2,coef = "h1TreatmentFluoxetine",number = 30)
saveRDS(h1fit2,"../FLX_datasets/GSE48951/DE_h1_GSE48951.rds")

h2Names=h2exGSE$geo_accession
h2Treatment=factor(h2exGSE$`drug:ch1`,levels=levels(as.factor(h2exGSE$`drug:ch1`))[c(4,1,3,2,5)])
#h2RepGroup=factor(h2exGSE$RepGroup)
Designh2=model.matrix(~h2Treatment)
rownames(Designh2)=h2Names
h2fit=lmFit(h2exGSE, Designh2)
h2fit2=eBayes(h2fit)
topTable(h2fit2,coef = "h2TreatmentFluoxetine",number = 30)
saveRDS(h2fit2,"../FLX_datasets/GSE48951/DE_h2_GSE48951.rds")

h4Names=h4exGSE$geo_accession
h4Treatment=factor(h4exGSE$`drug:ch1`,levels=levels(as.factor(h4exGSE$`drug:ch1`))[c(4,1,3,2,5)])
#h4RepGroup=factor(h4exGSE$RepGroup)
Designh4=model.matrix(~h4Treatment)
rownames(Designh4)=h4Names
h4fit=lmFit(h4exGSE, Designh4)
h4fit2=eBayes(h4fit)
topTable(h4fit2,coef = "h4TreatmentFluoxetine",number = 30)
saveRDS(h4fit2,"../FLX_datasets/GSE48951/DE_h4_GSE48951.rds")

h8Names=h8exGSE$geo_accession
h8Treatment=factor(h8exGSE$`drug:ch1`,levels=levels(as.factor(exGSE$`drug:ch1`))[c(4,1,3,2,5)])
#h8RepGroup=factor(h8exGSE$RepGroup)
Designh8=model.matrix(~h8Treatment)
rownames(Designh8)=h8Names
h8fit=lmFit(h8exGSE, Designh8)
h8fit2=eBayes(h8fit)
topTable(h8fit2,coef = "h8TreatmentFluoxetine",number = 30)
saveRDS(h8fit2,"../FLX_datasets/GSE48951/DE_h8_GSE48951.rds")

```

## Differential Expression Analysis

Volcano plots

```{r Volcano Plots}
volcanoplot(fit2,coef = "TreatmentNaive",main="Naive vs Control")
volcanoplot(fit2,coef = "TreatmentFluoxetine",main="Fluoxetine vs Control")

```

```{r}
volcanoplot(h1fit2,coef = "h1TreatmentNaive",main="h1 TreatOnly Naive vs Control")
volcanoplot(h1fit2,coef = "h1TreatmentFluoxetine",main="h1 TreatOnly Fluoxetine vs Control")

volcanoplot(h2fit2,coef = "h2TreatmentNaive",main="h2 TreatOnly Naive vs Control")
volcanoplot(h2fit2,coef = "h2TreatmentFluoxetine",main="h2 TreatOnly Fluoxetine vs Control")

volcanoplot(h4fit2,coef = "h4TreatmentNaive",main="h4 TreatOnly Naive vs Control")
volcanoplot(h4fit2,coef = "h4TreatmentFluoxetine",main="h4 TreatOnly Fluoxetine vs Control")

volcanoplot(h8fit2,coef = "h8TreatmentNaive",main="h8 TreatOnly Naive vs Control")
volcanoplot(h8fit2,coef = "h8TreatmentFluoxetine",main="h8 TreatOnly Fluoxetine vs Control")

```

## Gene Set Enrichment Analysis

Use fgsea to analyze gene set enrichment.

```{r Remove Duplicate Genes}
UniqueGenes=data.frame(AvgExpr=rowMeans(exprs(exGSE)),GENE_SYMBOL=exGSE@featureData@data$Symbol,Loci=exGSE@featureData@data$ID)
UniqueGenes2=arrange(UniqueGenes,desc(AvgExpr))%>%filter(!duplicated(GENE_SYMBOL))%>%filter(GENE_SYMBOL!="")
ensembl=useEnsembl(biomart="genes",dataset = "mmusculus_gene_ensembl")
GenesMouse=getBM(mart=ensembl,attributes = c("ensembl_gene_id","external_gene_name","entrezgene_id"))
UniqueGenes2$MouseEnsembl=GenesMouse$ensembl_gene_id[match(UniqueGenes2$GENE_SYMBOL,GenesMouse$external_gene_name)]
UniqueGenes3=filter(UniqueGenes2,MouseEnsembl!="")

```

```{r GSEA using fgsea}
#Pathways list using mouse Ensembl gene IDs
CPDBpaths=read_cpdb_tab("CPDB_pathways_genes_mouse.tab")
#GSEA
StatsFilter=UniqueGenes3%>%mutate(t=fit2$t[,"TreatmentFluoxetine"][match(UniqueGenes3$Loci,rownames(fit2$t))])
tstats=StatsFilter$t
names(tstats)=StatsFilter$MouseEnsembl
GeneEnrich=fgsea(pathways = CPDBpaths, stats = tstats, minSize  = 10)
head(arrange(GeneEnrich,padj),n=20)
plotEnrichment(CPDBpaths[["Formyl peptide receptors bind formyl peptides and many other ligands | Reactome"]], tstats)
saveRDS(GeneEnrich,"../FLX_datasets/GSE48951/GSEA_GSE48951.rds")

#GSEA h1
h1StatsFilter=UniqueGenes3%>%mutate(t=h1fit2$t[,"h1TreatmentFluoxetine"][match(UniqueGenes3$Loci,rownames(h1fit2$t))])
h1tstats=h1StatsFilter$t
names(h1tstats)=h1StatsFilter$MouseEnsembl
h1GeneEnrich=fgsea(pathways = CPDBpaths, stats = h1tstats, minSize  = 10)
head(arrange(h1GeneEnrich,padj),n=20)
saveRDS(h1GeneEnrich,"../FLX_datasets/GSE48951/GSEA_h1_GSE48951.rds")

#GSEA h2
h2StatsFilter=UniqueGenes3%>%mutate(t=h2fit2$t[,"h2TreatmentFluoxetine"][match(UniqueGenes3$Loci,rownames(h2fit2$t))])
h2tstats=h2StatsFilter$t
names(h2tstats)=h2StatsFilter$MouseEnsembl
h2GeneEnrich=fgsea(pathways = CPDBpaths, stats = h2tstats, minSize  = 10)
head(arrange(h2GeneEnrich,padj),n=20)
saveRDS(h2GeneEnrich,"../FLX_datasets/GSE48951/GSEA_h2_GSE48951.rds")

#GSEA h4
h4StatsFilter=UniqueGenes3%>%mutate(t=h4fit2$t[,"h4TreatmentFluoxetine"][match(UniqueGenes3$Loci,rownames(h4fit2$t))])
h4tstats=h4StatsFilter$t
names(h4tstats)=h4StatsFilter$MouseEnsembl
h4GeneEnrich=fgsea(pathways = CPDBpaths, stats = h4tstats, minSize  = 10)
head(arrange(h4GeneEnrich,padj),n=20)
saveRDS(h4GeneEnrich,"../FLX_datasets/GSE48951/GSEA_h4_GSE48951.rds")

#GSEA h8
h8StatsFilter=UniqueGenes3%>%mutate(t=h8fit2$t[,"h8TreatmentFluoxetine"][match(UniqueGenes3$Loci,rownames(h8fit2$t))])
h8tstats=h8StatsFilter$t
names(h8tstats)=h8StatsFilter$MouseEnsembl
h8GeneEnrich=fgsea(pathways = CPDBpaths, stats = h8tstats, minSize  = 10)
head(arrange(h8GeneEnrich,padj),n=20)
saveRDS(h8GeneEnrich,"../FLX_datasets/GSE48951/GSEA_h8_GSE48951.rds")


```

```{r Heatmaps GSEA}
TargetGenes=CPDBpaths[["Formyl peptide receptors bind formyl peptides and many other ligands | Reactome"]]
TargetTranscripts=UniqueGenes3$Loci[match(TargetGenes,UniqueGenes3$MouseEnsembl)][!is.na(TargetTranscripts)]
ExSubset=filter(as.data.frame(exprs(exGSE)),rownames(exGSE)%in%TargetTranscripts)

ColumnNames=data.frame(Timepoint=exGSE$`timepoint:ch1`,Treatment=exGSE$`drug:ch1`)
rownames(ColumnNames)=exGSE$geo_accession
pheatmap(ExSubset,annotation_col = ColumnNames,scale = "row")

```

