---
title: "GSE83386 Analysis"
author: "David Cooper"
date: "2022-09-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(GEOquery)
library(limma)
library("affycoretools")
library(affy)
library(tidyverse)
library(fgsea)
library(data.table)
library(preprocessCore)
library(pheatmap)
source("read_cpdb_tab.R")

```

## Data Acquisition

Use GEOquery to obtain the GEO series GSE83386. GSEMatrix=FALSE will pull out all the sample information as a GSE object. GSEMatrix=TRUE is the default and will provide a list of expression sets. Can use [[1]] to pull out the GSE object if there is only one. exprs() will return just the expression data and can be used to log transform the data if desired. 
https://bioconductor.org/packages/release/bioc/vignettes/GEOquery/inst/doc/GEOquery.html

```{r Get ExpressionSets}
GSEname="GSE83386"
GSE83386=getGEO(GSEname)
exGSE83386=GSE83386[[1]]
exprs(exGSE83386)=log2(exprs(exGSE83386))

```

## Quality Control Analyses 

Compare samples with boxplots and PCA to assess the quality across samples. Normalized datasets should have the same median across the samples. The boxplot will show if there are any samples that differ from the rest. 

```{r Boxplots}
#Boxplot with all samples, log 2 transformed
boxplot(exprs(exGSE83386),las=2)
#Quantile plot with all samples, log 2 transformed
qs=t(apply(exprs(exGSE83386),2,quantile,prob=c(0.05,0.25,0.5,0.75,0.95)))
matplot(qs,type="l",lty=1)

```


```{r PCA}
#Samples all individual
plotPCA(exGSE83386,outside=TRUE)
#samples grouped treatment and control
plotPCA(exGSE83386, groups = as.numeric(as.factor(exGSE83386@phenoData@data$characteristics_ch1.2)), groupnames = gsub("treatment: ","",levels(as.factor(exGSE83386@phenoData@data$characteristics_ch1.2))),outside=TRUE)
#samples grouped by cell line
plotPCA(exGSE83386, groups = as.numeric(as.factor(exGSE83386@phenoData@data$characteristics_ch1.1)), groupnames = gsub("cell line: ","",levels(as.factor(exGSE83386@phenoData@data$characteristics_ch1.1))),outside=TRUE)
#samples grouped by responder type
plotPCA(exGSE83386, groups = as.numeric(as.factor(exGSE83386@phenoData@data$`clinical treatment outcome:ch1`)), groupnames = levels(as.factor(exGSE83386@phenoData@data$`clinical treatment outcome:ch1`)),outside=TRUE)

```

## Data normalization

Normalize raw data using quantile normalization. Raw data for GSE83386 is not formatted in CEL files as needed for input into rma.

```{r Quantile Normalization}
qexGSE83386=exGSE83386
exprs(qexGSE83386)=normalize.quantiles(exprs(exGSE83386))
#Boxplot with all samples, log 2 transformed
boxplot(exprs(qexGSE83386),las=2)
#Quantile plot with all samples, log 2 transformed
qs=t(apply(exprs(qexGSE83386),2,quantile,prob=c(0.05,0.25,0.5,0.75,0.95)))
matplot(qs,type="l",lty=1)
#Samples all individual
plotPCA(qexGSE83386,outside=TRUE)
#samples grouped treatment and control
plotPCA(qexGSE83386, groups = as.numeric(as.factor(exGSE83386@phenoData@data$characteristics_ch1.2)), groupnames = gsub("treatment: ","",levels(as.factor(exGSE83386@phenoData@data$characteristics_ch1.2))),outside=TRUE)
#samples grouped by cell line
plotPCA(qexGSE83386, groups = as.numeric(as.factor(exGSE83386@phenoData@data$characteristics_ch1.1)), groupnames = gsub("cell line: ","",levels(as.factor(exGSE83386@phenoData@data$characteristics_ch1.1))),outside=TRUE)
#samples grouped by responder type
plotPCA(qexGSE83386, groups = as.numeric(as.factor(exGSE83386@phenoData@data$`clinical treatment outcome:ch1`)), groupnames = levels(as.factor(exGSE83386@phenoData@data$`clinical treatment outcome:ch1`)),outside=TRUE)

```

## Remove Low-expressed genes

Removal of gene loci without expression above a threshold in at least half of the samples. No sample has an expression level less than 2.5, so no filtering was done. 

```{r}
Threshold=1 #What should a low expression threshold be?
for(i in 1:as.numeric(ncol(GSE83386[[1]]))){print(min(GSE83386[[1]][,i]@assayData[["exprs"]]))}

```

## Expression Analysis

Use limma to analyze expression.First attempt following instructions in 9.2 of the limmaUsersGuide to compare fluoxetine vs. control. Next attempt considering the paired patient samples (section 9.4.1). >limmaUsersGuide() to open the users guide manual.

```{r Two Group Analysis}
Names=pData(exGSE83386)[,2]
Treatment=factor(pData(exGSE83386)[,12])
Design=model.matrix(~Treatment)
rownames(Design)=Names
fit=lmFit(exGSE83386, Design)
fit2=eBayes(fit)
topTable(fit2)

```

```{r Paired Patient Samples Analysis}
PatientPair=factor(pData(exGSE83386)[,11])
DesignPair=model.matrix(~PatientPair+Treatment)
rownames(DesignPair)=Names
pairfit=lmFit(exGSE83386,DesignPair)
pairfit2=eBayes(pairfit)
topTable(pairfit2,coef = "Treatmenttreatment: fluoxetine")

```

## Expression Analysis Quantile Normalized Data

Compare treatment vs. control with paired samples with all samples or responders and non-responders separately. Evaluate the interaction between responder cell lines and treatment.

```{r Paired Patient Samples Analysis 2}
Names=pData(exGSE83386)[,2]
Treatment=factor(pData(exGSE83386)[,12])
TreatResponse=factor(paste(gsub(pattern = "treatment: ",replacement = "",x = Treatment),factor(pData(exGSE83386)[,35]),sep = "_"),levels = c("control_non-responder","control_responder","fluoxetine_non-responder","fluoxetine_responder"))

#All samples
PatientPair=factor(pData(qexGSE83386)[,11])
DesignPair=model.matrix(~PatientPair+Treatment)
rownames(DesignPair)=Names
pairfit=lmFit(qexGSE83386,DesignPair)
pairfit2=eBayes(pairfit)
topTable(pairfit2,coef = "Treatmenttreatment: fluoxetine")
saveRDS(pairfit2,"../FLX_datasets/GSE83386/DE_All_GSE83386.rds")

#Responders
qexResponders=qexGSE83386[,pData(qexGSE83386)[,35]=="responder"]
rPatientPair=factor(pData(qexResponders)[,11])
rTreatment=factor(pData(qexResponders)[,12])
rDesignPair=model.matrix(~0+rPatientPair+rTreatment)
rNames=pData(qexResponders)[,2]
rownames(rDesignPair)=rNames
rpairfit=lmFit(qexResponders,rDesignPair)
rpairfit2=eBayes(rpairfit)
topTable(rpairfit2,coef = "rTreatmenttreatment: fluoxetine")
saveRDS(rpairfit2,"../FLX_datasets/GSE83386/DE_Res_GSE83386.rds")

#Nonresponders
qexNon=qexGSE83386[,pData(qexGSE83386)[,35]=="non-responder"]
nPatientPair=factor(pData(qexNon)[,11])
nTreatment=factor(pData(qexNon)[,12])
nDesignPair=model.matrix(~0+nPatientPair+nTreatment)
nNames=pData(qexNon)[,2]
rownames(nDesignPair)=nNames
npairfit=lmFit(qexNon,nDesignPair)
npairfit2=eBayes(npairfit)
topTable(npairfit2,coef = "nTreatmenttreatment: fluoxetine")
saveRDS(npairfit2,"../FLX_datasets/GSE83386/DE_Non_GSE83386.rds")

#Responders vs Nonresponders
DesignResponse=model.matrix(~0+TreatResponse)
rownames(DesignResponse)=Names
colnames(DesignResponse)=c("CNR","CR","FNR","FR")
Responsefit=lmFit(qexGSE83386, DesignResponse)
contrasts_Response=makeContrasts(FR - FNR, FR - CR, FNR - CNR, CR - CNR, levels = DesignResponse)  
Responsefit2=contrasts.fit(Responsefit,contrasts_Response)
Responsefit2=eBayes(Responsefit2)
topTable(Responsefit2,coef = "FR - FNR")
saveRDS(Responsefit2,"../FLX_datasets/GSE83386/DE_ResVNon_GSE83386.rds")

```

## Differential Expression Analysis

Volcano plots for responders and non-responders.
Scatter plot stats for responders vs non-responders in a merged table

```{r}
pairfit2=readRDS("../FLX_datasets/GSE83386/DE_All_GSE83386.rds")
rpairfit2=readRDS("../FLX_datasets/GSE83386/DE_Res_GSE83386.rds")
npairfit2=readRDS("../FLX_datasets/GSE83386/DE_Non_GSE83386.rds")
Responsefit2=readRDS("../FLX_datasets/GSE83386/DE_ResVNon_GSE83386.rds")

colnames(pairfit2$coefficients)
colnames(rpairfit2$coefficients)
colnames(npairfit2$coefficients)
colnames(Responsefit2$coefficients)

summary(decideTests(pairfit2))
summary(decideTests(rpairfit2))
summary(decideTests(npairfit2))
summary(decideTests(Responsefit2))


```

```{r Volcano Plots}
volcanoplot(npairfit2,coef = "nTreatmenttreatment: fluoxetine",main="Non-Responders")
volcanoplot(rpairfit2,coef = "rTreatmenttreatment: fluoxetine",main="Responders")

```

```{r Scatter Plot}
all(rownames(npairfit2$coefficients)==rownames(rpairfit2$coefficients))
NandRfit=cbind(npairfit2$coefficients,rpairfit2$coefficients)
ggplot(as.data.frame(NandRfit))+
  geom_point(mapping=aes(x=`nTreatmenttreatment: fluoxetine`,y=`rTreatmenttreatment: fluoxetine`))+
  theme_classic()
colnames(NandRfit)
class(NandRfit)

```
## Investigating High Fold Change genes in responder group

What genes are more highly expressed, but not highly significantly overexpressed, in the responder group?

```{r Heatmap Reponder Group}
#Obtain gene list for genes with log2 FC greater than 2 based on rpairfit2 table.
RespondHighFC=topTable(rpairfit2,coef = "rTreatmenttreatment: fluoxetine",number=200,sort.by = "logFC")
GeneList=filter(RespondHighFC, logFC>=2 & REFSEQ!="")%>%select(REFSEQ)
ResponderEx=as.data.frame(exprs(qexResponders))
ExSubset=ResponderEx[rownames(ResponderEx)%in%rownames(GeneList),]
rownames(ExSubset)=GeneList$REFSEQ
ColumnNames=data.frame(CellLine=pData(qexResponders)[,11],Treatment=pData(qexResponders)[,12])
rownames(ColumnNames)=pData(qexResponders)[,2]
pheatmap(ExSubset,annotation_col = ColumnNames)

```

## Gene Set Enrichment Analysis

Use fgsea to analyze gene set enrichment.

```{r Remove Duplicate Genes}
#Get the average expression across all samples for each locus
UniqueGenes=data.frame(AvgExpr=rowMeans(exprs(exGSE83386)),GENE_SYMBOL=exGSE83386@featureData@data[["GENE_SYMBOL"]],Loci=rownames(exprs(exGSE83386)))
#filter the expression set to only include the rows with the highest average expression using the loci (default) row names
UniqueGenes2=group_by(UniqueGenes,GENE_SYMBOL)%>%filter(AvgExpr==max(AvgExpr))%>%filter(GENE_SYMBOL!="")

#An alternative method to get the unique genes
UniqueGenes3=arrange(UniqueGenes,desc(AvgExpr))%>%filter(!duplicated(GENE_SYMBOL))%>%filter(GENE_SYMBOL!="")
all(arrange(UniqueGenes2,desc(AvgExpr))==UniqueGenes3)

```

```{r GSEA using fgsea}
#Pathways list using Gene_Symbols
CPDBpaths=read_cpdb_tab("CPDB_pathways_genes_symbol.tab")

#Pooled treatment vs control (t stat and gene symbols) using filtered genes list
PooledFilter=topTable(pairfit2,coef = "Treatmenttreatment: fluoxetine",number = Inf)%>%filter(ID%in%UniqueGenes2$Loci)
tstats=PooledFilter$t
names(tstats)=PooledFilter$GENE_SYMBOL
GeneEnrich=fgsea(pathways = CPDBpaths, stats = tstats, minSize  = 10)
saveRDS(GeneEnrich,"../FLX_datasets/GSE83386/GSEA_Pooled_GSE83386.rds")

#Stats vector for responders, patient-pairs treatment vs control (t stat and gene symbols) using filtered genes list
RespondersFilter=topTable(rpairfit2,coef = "rTreatmenttreatment: fluoxetine",number = Inf)%>%filter(ID%in%UniqueGenes2$Loci)
rtstats=RespondersFilter$t
names(rtstats)=RespondersFilter$GENE_SYMBOL
rGeneEnrich=fgsea(pathways = CPDBpaths, stats = rtstats, minSize  = 10)
#head(arrange(rGeneEnrich,padj),n=20)
#plotEnrichment(CPDBpaths[["Apoptosis - Homo sapiens (human) | KEGG"]], rtstats)
saveRDS(rGeneEnrich,"../FLX_datasets/GSE83386/GSEA_Res_GSE83386.rds")

#Stats vector for non-responders, patient-pairs treatment vs control (t stat and gene symbols) using filtered genes list
NonFilter=topTable(npairfit2,coef = "nTreatmenttreatment: fluoxetine",number = Inf)%>%filter(ID%in%UniqueGenes2$Loci)
ntstats=NonFilter$t
names(ntstats)=NonFilter$GENE_SYMBOL
nGeneEnrich=fgsea(pathways = CPDBpaths, stats = ntstats, minSize  = 10)
#head(arrange(nGeneEnrich,padj),n=20)
#plotEnrichment(CPDBpaths[["Apoptosis - Homo sapiens (human) | KEGG"]], ntstats)
saveRDS(nGeneEnrich,"../FLX_datasets/GSE83386/GSEA_Non_GSE83386.rds")

#Responders vs Non-responders
VFilter=topTable(Responsefit2,coef = "FR - FNR",number = Inf)%>%filter(ID%in%UniqueGenes2$Loci)
vtstats=VFilter$t
names(vtstats)=VFilter$GENE_SYMBOL
vGeneEnrich=fgsea(pathways = CPDBpaths, stats = vtstats, minSize  = 10)
#head(arrange(nGeneEnrich,padj),n=20)
#plotEnrichment(CPDBpaths[["Apoptosis - Homo sapiens (human) | KEGG"]], ntstats)
saveRDS(vGeneEnrich,"../FLX_datasets/GSE83386/GSEA_ResVNon_GSE83386.rds")

#Responders vs Non-responders
XFilter=topTable(Responsefit2,coef = "CR - CNR",number = Inf)%>%filter(ID%in%UniqueGenes2$Loci)
Xtstats=XFilter$t
names(Xtstats)=XFilter$GENE_SYMBOL
XGeneEnrich=fgsea(pathways = CPDBpaths, stats = Xtstats, minSize  = 10)
saveRDS(XGeneEnrich,"../FLX_datasets/GSE83386/GSEA_UnResVNon_GSE83386.rds")

```


```{r GSEA Res and Non combined}
#Combine and Compare responders vs nonresponders
all(nGeneEnrich$pathway==rGeneEnrich$pathway)
nTrunc=select(nGeneEnrich,pathway,NES)
colnames(nTrunc)=c("npathway","nNES")
NandRgsea=cbind(nTrunc,rGeneEnrich)
ggplot(NandRgsea)+
  geom_point(mapping=aes(x=nNES,y=NES))+
  theme_classic()


```

```{r Heatmaps GSEA}
TargetGenes=CPDBpaths[["Apoptosis - Homo sapiens (human) | KEGG"]]

RespondersExprs=as.data.frame(exprs(qexResponders))
URespondersExprs=filter(RespondersExprs,rownames(RespondersExprs)%in%UniqueGenes2$Loci)
rownames(URespondersExprs)=UniqueGenes2$GENE_SYMBOL
rExSubset=URespondersExprs[rownames(URespondersExprs)%in%TargetGenes,]
rColumnNames=data.frame(CellLine=pData(qexResponders)[,11],Treatment=pData(qexResponders)[,12])
rownames(rColumnNames)=pData(qexResponders)[,2]
pheatmap(rExSubset,annotation_col = rColumnNames,scale = "row")

NonExprs=as.data.frame(exprs(qexNon))
UNonExprs=filter(NonExprs,rownames(NonExprs)%in%UniqueGenes2$Loci)
rownames(UNonExprs)=UniqueGenes2$GENE_SYMBOL
nExSubset=UNonExprs[rownames(UNonExprs)%in%TargetGenes,]
nColumnNames=data.frame(CellLine=pData(qexNon)[,11],Treatment=pData(qexNon)[,12])
rownames(nColumnNames)=pData(qexNon)[,2]
pheatmap(nExSubset,annotation_col = nColumnNames,scale = "row") 

```

