---
title: "GSE146446 Analysis"
author: "David Cooper"
date: "2022-09-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(GEOquery)
library(limma)
library("affycoretools")
library(affy)
library(tidyverse)
library(fgsea)
library(data.table)
library(preprocessCore)
library(pheatmap)
source("read_cpdb_tab.R")

```

## Data Acquisition

Use GEOquery to obtain the GEO series GSE83386. GSEMatrix=FALSE will pull out all the sample information as a GSE object. GSEMatrix=TRUE is the default and will provide a list of expression sets. Can use [[1]] to pull out the GSE object if there is only one. exprs() will return just the expression data and can be used to log transform the data if desired. 
https://bioconductor.org/packages/release/bioc/vignettes/GEOquery/inst/doc/GEOquery.html

```{r Get ExpressionSets}
set.seed(123)
GSEname="GSE146446"
GSE=getGEO(GSEname)
exGSE=GSE[[1]]
#exprs(exGSE)=log2(exprs(exGSE))

```

## Quality Control Analyses 

Compare samples with boxplots and PCA to assess the quality across samples. Normalized datasets should have the same median across the samples. The boxplot will show if there are any samples that differ from the rest. 

```{r Boxplots}
#Boxplot with all samples, log 2 transformed
#boxplot(exprs(exGSE),las=2)

#Quantile plot with all samples, log 2 transformed
#qs=t(apply(exprs(exGSE),2,quantile,prob=c(0.05,0.25,0.5,0.75,0.95)))
#matplot(qs,type="l",lty=1)

```

```{r PCA}
#Samples all individual
plotPCA(exGSE,outside=TRUE)
#samples grouped treatment and control
plotPCA(exGSE, groups = as.numeric(as.factor(exGSE@phenoData@data$characteristics_ch1.2)), groupnames = gsub("treatment: ","",levels(as.factor(exGSE@phenoData@data$characteristics_ch1.2))),outside=TRUE)
#samples grouped by Timepoint
plotPCA(exGSE, groups = as.numeric(as.factor(exGSE@phenoData@data$characteristics_ch1.1)), groupnames = gsub("cell line: ","",levels(as.factor(exGSE@phenoData@data$characteristics_ch1.1))),outside=TRUE)
#samples grouped by responder type
plotPCA(exGSE, groups = as.numeric(as.factor(exGSE@phenoData@data$characteristics_ch1.5)), groupnames = levels(as.factor(exGSE@phenoData@data$characteristics_ch1.5)),outside=TRUE)
#
plotPCA(exGSE, groups = as.numeric(as.factor(exGSE@phenoData@data$source_name_ch1)), groupnames = levels(as.factor(exGSE@phenoData@data$source_name_ch1)),outside=TRUE)

```

## Differential Expression Analysis

Groups:
DLX_T0_0  21
DLX_T0_1
DLX_T8_0  75
DLX_T8_1
PLB_T0_0  63
PLB_T0_1
PLB_T8_0  44
PLB_T8_1

Comparisons:
Dlx responders vs nonresponders (treated)
Dlx responders vs nonresponders (untreated)
Placebo responders vs nonresponders (treated)
Placebo responders vs nonresponders (untreated)
Dlx treated vs untreated (all)
Placebo treated vs untreated (all)

```{r Two Group Analysis}
Names=pData(exGSE)$geo_accession
TreatmentResponse=factor(pData(exGSE)$source_name_ch1)
Treatment=factor(str_sub(pData(exGSE)$source_name_ch1,1,6))
PatientPair=factor(gsub("subject_id: ","",pData(exGSE)$characteristics_ch1))

#Response & TvU for responders and non-responders
Design=model.matrix(~0+TreatmentResponse)
rownames(Design)=Names
colnames(Design)=c("DLX_T0_0", "DLX_T0_1", "DLX_T8_0", "DLX_T8_1", "PLB_T0_0", "PLB_T0_1", "PLB_T8_0", "PLB_T8_1")
fit=lmFit(exGSE,Design)
contrasts=makeContrasts(DLX_T8_1 - DLX_T0_1, DLX_T8_0 - DLX_T0_0, DLX_T8_1 - DLX_T8_0, DLX_T0_1 - DLX_T0_0, 
                        PLB_T8_1 - PLB_T0_1, PLB_T8_0 - PLB_T0_0, PLB_T8_1 - PLB_T8_0, PLB_T0_1 - PLB_T0_0, levels = Design)  
fit2=contrasts.fit(fit,contrasts)
fit2=eBayes(fit2)

saveRDS(fit2,"DE_Response_GSE146446.rds")

#head(fit2$coefficients)
#topTable(fit2,coef = "DLX_T8_1 - DLX_T0_1")

#TvU for all treated
Design2=model.matrix(~0+Treatment)
rownames(Design2)=Names
colnames(Design2)=c("DLX_T0", "DLX_T8", "PLB_T0", "PLB_T8")
fit3=lmFit(exGSE,Design2)
contrasts2=makeContrasts(DLX_T8 - DLX_T0, PLB_T8 - PLB_T0, levels = Design2)  
fit4=contrasts.fit(fit3,contrasts2)
fit4=eBayes(fit4)

saveRDS(fit4,"DE_TreatedAll_GSE146446.rds")

```

```{r Volcano Plots}
volcanoplot(fit2,coef = "DLX_T8_1 - DLX_T8_0")

```

## Gene Set Enrichment Analysis

Use fgsea to analyze gene set enrichment.

```{r Remove Duplicate Genes}
#Get the average expression across all samples for each locus
UniqueGenes=data.frame(AvgExpr=rowMeans(exprs(exGSE)),GENE_SYMBOL=exGSE@featureData@data$Symbol,Loci=rownames(exprs(exGSE)))

#filter the expression set to only include the rows with the highest average expression using the loci (default) row names
UniqueGenes2=group_by(UniqueGenes,GENE_SYMBOL)%>%filter(AvgExpr==max(AvgExpr))%>%filter(GENE_SYMBOL!="")

#An alternative method to get the unique genes
#UniqueGenes3=arrange(UniqueGenes,desc(AvgExpr))%>%filter(!duplicated(GENE_SYMBOL))%>%filter(GENE_SYMBOL!="")
#all(arrange(UniqueGenes2,desc(AvgExpr))==UniqueGenes3)

```

```{r GSEA using fgsea}
#Pathways list using Gene_Symbols
CPDBpaths=read_cpdb_tab("CPDB_pathways_genes_symbol.tab")

DElist=list()

#Dlx responders vs nonresponders (treated)
Dlx8hResponse=topTable(fit2,coef = "DLX_T8_1 - DLX_T8_0",number = Inf)%>%filter(ID%in%UniqueGenes2$Loci)
DElist$DRN8=Dlx8hResponse[Dlx8hResponse$P.Value<0.05,]$Symbol
DEbackground=Dlx8hResponse$Symbol
tstats=Dlx8hResponse$t
names(tstats)=Dlx8hResponse$Symbol
GeneEnrich=fgsea(pathways = CPDBpaths, stats = tstats, minSize  = 10, nPermSimple=10000)
saveRDS(GeneEnrich,"GSEA_Dlx8hResponse_GSE146446.rds")

#Dlx responders vs nonresponders (untreated)
Dlx0hResponse=topTable(fit2,coef = "DLX_T0_1 - DLX_T0_0",number = Inf)%>%filter(ID%in%UniqueGenes2$Loci)
DElist$DRN0=Dlx0hResponse[Dlx0hResponse$P.Value<0.05,]$Symbol
tstats=Dlx0hResponse$t
names(tstats)=Dlx0hResponse$Symbol
GeneEnrich=fgsea(pathways = CPDBpaths, stats = tstats, minSize  = 10, nPermSimple=10000)
saveRDS(GeneEnrich,"GSEA_Dlx0hResponse_GSE146446.rds")

#Placebo responders vs nonresponders (treated)
Plb8hResponse=topTable(fit2,coef = "PLB_T8_1 - PLB_T8_0",number = Inf)%>%filter(ID%in%UniqueGenes2$Loci)
DElist$PRN8=Plb8hResponse[Plb8hResponse$P.Value<0.05,]$Symbol
tstats=Plb8hResponse$t
names(tstats)=Plb8hResponse$Symbol
GeneEnrich=fgsea(pathways = CPDBpaths, stats = tstats, minSize  = 10, nPermSimple=10000)
saveRDS(GeneEnrich,"GSEA_Plb8hResponse_GSE146446.rds")

#Placebo responders vs nonresponders (untreated)
Plb0hResponse=topTable(fit2,coef = "PLB_T0_1 - PLB_T0_0",number = Inf)%>%filter(ID%in%UniqueGenes2$Loci)
DElist$PRN0=Plb0hResponse[Plb0hResponse$P.Value<0.05,]$Symbol
tstats=Plb0hResponse$t
names(tstats)=Plb0hResponse$Symbol
GeneEnrich=fgsea(pathways = CPDBpaths, stats = tstats, minSize  = 10, nPermSimple=10000)
saveRDS(GeneEnrich,"GSEA_Plb0hResponse_GSE146446.rds")

#Dlx treated vs untreated (all)
DlxTreatment=topTable(fit4,coef = "DLX_T8 - DLX_T0",number = Inf)%>%filter(ID%in%UniqueGenes2$Loci)
DElist$DTU=DlxTreatment[DlxTreatment$P.Value<0.05,]$Symbol
tstats=DlxTreatment$t
names(tstats)=DlxTreatment$Symbol
GeneEnrich=fgsea(pathways = CPDBpaths, stats = tstats, minSize  = 10, nPermSimple=10000)
saveRDS(GeneEnrich,"GSEA_DlxTreatment_GSE146446.rds")

#Placebo treated vs untreated (all)
PlbTreatment=topTable(fit4,coef = "PLB_T8 - PLB_T0",number = Inf)%>%filter(ID%in%UniqueGenes2$Loci)
DElist$PTU=PlbTreatment[PlbTreatment$P.Value<0.05,]$Symbol
tstats=PlbTreatment$t
names(tstats)=PlbTreatment$Symbol
GeneEnrich=fgsea(pathways = CPDBpaths, stats = tstats, minSize  = 10, nPermSimple=10000)
saveRDS(GeneEnrich,"GSEA_PlbTreatment_GSE146446.rds")

write.table(t(plyr::ldply(DElist,rbind)),"GSE146446-DElist.txt",sep = "\t",na = "",quote = FALSE,col.names = FALSE,row.names = FALSE)
write.table(DEbackground,"GSE146446-DEbackground.txt",quote = FALSE,col.names = FALSE,row.names = FALSE)

```

```{r Heatmaps GSEA}
TargetGenes=CPDBpaths[["Lysosome - Homo sapiens (human) | KEGG"]]

Exprs=as.data.frame(exprs(exGSE))
UExprs=filter(Exprs,rownames(Exprs)%in%UniqueGenes2$Loci)
rownames(UExprs)=UniqueGenes2$GENE_SYMBOL
ExSubset=UExprs[rownames(UExprs)%in%TargetGenes,]
ColumnNames=data.frame(CellLine=pData(exGSE)[,10],Treatment=pData(exGSE)[,8])
rownames(ColumnNames)=pData(exGSE)[,2]
pheatmap(ExSubset,annotation_col = ColumnNames,scale = "row")

```
