---
title: "Compare Human Studies"
author: "Caleb Class"
date: "2024-11-01"
output: html_document
---

```{r}
library(tidyverse)
library(plotly)

source("../FLX RMD/read_cpdb_tab.R")
reactome_hs <- readRDS("../FLX RMD/Reactome_HS_withTopLevel.rds")
cpdb <- read_cpdb_tab("../FLX RMD/CPDB_pathways_genes_mouse.tab")
#names(cpdb) <- gsub(" \\|.*| \\- Mus.*", "", names(cpdb))
npgColors <- readRDS("../npgColors.rds")
npgFill <- readRDS("../npgFill.rds")


```


# Response vs. Non-response
## Treated

Both datasets included R vs. NR comparisons: GSE146446 (Belzeaux/Fiori et al) includes duloxetine responders
vs. non-responders after treatment, PMID26008736 (Jansen et al, 2015) includes 
remitted vs. current MDD -- however, only a subset of patients from each
group reported current antidepressant use (some may have previously).

```{r}

# Meta-analysis results
dat <- readRDS("../MetaDE RDS/AllSFRNgsea.rds")
pvals <- dat[,1:9]
summariesRN <- dat[,10:15]

# Fluoxetine results (GSE83386, included in meta-analysis)
flxRN <- readRDS("../FLX_datasets/GSE83386/GSEA_ResVNon_GSE83386.rds")
# Convert KEGG names to match those in meta-analysis
flxRN$pathway <- gsub(" - Homo sapiens \\(human\\)", "", flxRN$pathway)

# Duloxetine results (GSE146446)
dlxRN <- readRDS("../AdditionalDatasets/GSEA_Dlx8hResponse_GSE146446.rds")
dlxRN$pathway <- gsub(" - Homo sapiens \\(human\\)", "", dlxRN$pathway)

# Large study results (Jansen et al, included SSRI, TCA, SNRI use)
janRN <- readRDS("../AdditionalDatasets/GSEA_RemCurr_PMID26008736.rds")
janRN$pathway <- gsub(" - Homo sapiens \\(human\\)", "", janRN$pathway)

# Merge results (keep all from meta-analysis)
mergedRN <- merge(summariesRN, flxRN, all.x = TRUE, 
                  by.x = "Pathway", by.y = "pathway", 
                  suffixes = c(".meta", ".flx"))

mergedRN <- merge(mergedRN, dlxRN, all.x = TRUE, 
                  by.x = "Pathway", by.y = "pathway", 
                  suffixes = c(".flx", ""))

mergedRN <- merge(mergedRN, janRN, all.x = TRUE, 
                  by.x = "Pathway", by.y = "pathway", 
                  suffixes = c(".dlx", ".jan"))

```

Venn diagrams overlapping w/ meta-analysis

```{r}

library(VennDiagram)
library(ggvenn)

fisherVenn <- list(Fisher=mergedRN$Pathway[mergedRN$Fish < 0.05 & !is.na(mergedRN$Fish)],
                   Breitfeld=mergedRN$Pathway[mergedRN$padj.flx < 0.05 & !is.na(mergedRN$padj.flx)],
                   Jansen=mergedRN$Pathway[mergedRN$padj.jan < 0.05 & !is.na(mergedRN$padj.jan)])

venn.diagram(fisherVenn,
             euler.d = TRUE, scaled=TRUE, 
             category=c("Fisher's\nMeta-analysis","Breitfeld et al.\n(Fluoxetine)","Jansen et al.\n(Naturalistic)"),
             lty=rep("solid", 3), 
             fill=c(alpha("#21B0FE",0.4), alpha("#ffca4e",0.4),alpha("#fc8c78",0.4)), 
             col=c("#21B0FE", "#ffca4e","#fc8c78"),
             cat.col=c("#21B0FE", "#ffca4e","#fc8c78"),
             cex=2, 
             cat.cex=2,
             cat.dist=c(0.15,0.03,0.16),
             cat.pos=c(200,160,0),
             margin=0.1,
             disable.logging=TRUE,
             filename = "../Figures/ComparisonFigures/Fisher_Human_Studies.tiff")


maxVenn <- list(MaxP=mergedRN$Pathway[mergedRN$Max < 0.05 & !is.na(mergedRN$Max)],
                   Breitfeld=mergedRN$Pathway[mergedRN$padj.flx < 0.05 & !is.na(mergedRN$padj.flx)],
                   Jansen=mergedRN$Pathway[mergedRN$padj.jan < 0.05 & !is.na(mergedRN$padj.jan)])

venn.diagram(maxVenn,
             euler.d = TRUE, scaled=TRUE, 
             category=c("Max-P\nMeta-analysis","Breitfeld et al.\n(Fluoxetine)","Jansen et al.\n(Naturalistic)"),
             lty=rep("solid", 3), 
             fill=c(alpha("#bf5747",0.4), alpha("#ffca4e",0.4),alpha("#fc8c78",0.4)), 
             col=c("#bf5747", "#ffca4e","#fc8c78"),
             cat.col=c("#bf5747", "#ffca4e","#fc8c78"),
             cex=2, 
             cat.cex=2,
             cat.dist=c(0.2,0.03,0.07),
             cat.pos=c(-20,180,20),
             margin=0.1,
             disable.logging=TRUE,
             filename = "../Figures/ComparisonFigures/MaxP_Human_Studies.tiff")


```

Compare direction of enrichment

```{r} 



```


Overlap differential expression results (none passed false discovery)

```{r}

library(limma)

# Only 1 human study:  Fluoxetine results (GSE83386, included in meta-analysis)
flxRN <- readRDS("../FLX_datasets/GSE83386/DE_ResVNon_GSE83386.rds")
flxRN <- topTable(flxRN,coef = "FR - FNR",number = Inf) %>%
  arrange(desc(AveExpr)) %>% filter(!duplicated(GENE_SYMBOL))

# Duloxetine results (GSE146446)
dlxRN <- readRDS("../AdditionalDatasets/DE_Response_GSE146446.rds")
dlxRN <- topTable(dlxRN,coef = "DLX_T8_1 - DLX_T8_0",number = Inf) %>%
  arrange(desc(AveExpr)) %>% filter(!duplicated(Symbol))

# Large study results (Jansen et al, included SSRI, TCA, SNRI use)
janRN <- readRDS("../AdditionalDatasets/PMID26008736DEtable.rds") %>%
  arrange(desc(Mean_Remitted + Mean_Current)) %>% filter(!duplicated(Gene))

# Merge results 
mergedRN <- merge(flxRN, dlxRN, all.x = TRUE, 
                  by.x = "GENE_SYMBOL", by.y = "Symbol", 
                  suffixes = c(".flx", ".dlx"))

mergedRN <- merge(mergedRN, janRN, all.x = TRUE, 
                  by.x = "GENE_SYMBOL", by.y = "Gene", 
                  suffixes = c(".dlx", ".jan"))

mergedRN <- mergedRN %>% select(starts_with("GENE"), 
                                starts_with("adj.P"), 
                                starts_with("logFC"), 
                                starts_with("FDR_"), 
                                starts_with("B_"))


```



## Prior to treatment

**See RvsN_preTreat report.**


# Treated vs. Untreated

Jansen et al. should not be used in this case, because their control group did not have MDD.


```{r}

datA <- readRDS("../MetaDE RDS/AllFTUgsea.rds")[,56:61]
datS <- readRDS("../MetaDE RDS/AllSFTUgsea.rds")[,14:19]

breitfeld <- readRDS("../FLX_datasets/GSE83386/GSEA_Pooled_GSE83386.rds")
breitfeld$pathway <- gsub(" - Homo sapiens \\(human\\)", "", breitfeld$pathway)

torres <- readRDS("../FLX_datasets/GSE128387/GSEA_GSE128387.rds")
torres$pathway <- gsub(" - Homo sapiens \\(human\\)", "", torres$pathway)

duloxetine <- readRDS("../AdditionalDatasets/GSEA_DlxTreatment_GSE146446.rds")
duloxetine$pathway <- gsub(" - Homo sapiens \\(human\\)", "", duloxetine$pathway)

mergedFTU <- merge(breitfeld, torres, all = TRUE, 
                  by = "pathway", 
                  suffixes = c(".breitfeldFLX", ""))

mergedFTU <- merge(mergedFTU, duloxetine, all = TRUE,
                   by = "pathway",
                   suffixes = c(".torresFLX", ".fioriDLX"))

mergedFTU <- mergedFTU[gsub(".*\\| ","", mergedFTU$pathway) %in% c("Reactome", "KEGG"),]


```


```{r}

library(VennDiagram)
library(ggvenn)

mergeVenn <- list(Breitfeld=mergedFTU$pathway[mergedFTU$padj.breitfeldFLX < 0.05 & !is.na(mergedFTU$padj.breitfeldFLX)],
                   Torres=mergedFTU$pathway[mergedFTU$padj.torresFLX < 0.05 & !is.na(mergedFTU$padj.torresFLX)],
                   Duloxetine=mergedFTU$pathway[mergedFTU$padj.fioriDLX < 0.05 & !is.na(mergedFTU$padj.fioriDLX)])

venn.diagram(mergeVenn,
             euler.d = TRUE, scaled=TRUE, 
             category=c("Breitfeld et al.\n(Fluoxetine)", "Torres et al.\n(Fluoxetine)","Belzeaux et al.\n(Duloxetine)"),
             lty=rep("solid", 3), 
             fill=c(alpha("#bf5747",0.4), alpha("#ffca4e",0.4),alpha("#fc8c78",0.4)), 
             col=c("#bf5747", "#ffca4e","#fc8c78"),
             cat.col=c("#bf5747", "#ffca4e","#fc8c78"),
             cex=2, 
             cat.cex=2,
             cat.dist=rep(0.12,3),
             #cat.pos=c(200,160,0),
             margin=0.1,
             disable.logging=TRUE,
             filename = "../Figures/ComparisonFigures/FTU_Human_Studies.tiff")




```
Summarize types of gene sets in overlap

```{r}

mergedFTU$ReactomeID <- reactome_hs$ID[match(gsub(" \\|.*", "", mergedFTU$pathway), reactome_hs$Name)]
mergedFTU$ReactomeTop <- reactome_hs$top_level_name[match(mergedFTU$ReactomeID, reactome_hs$ID)]
mergedFTU$ReactomeTop[substr(mergedFTU$pathway, nchar(mergedFTU$pathway)-3, nchar(mergedFTU$pathway)) == "KEGG"] <- "KEGG Database"
mergedFTU$ReactomeTop[!(mergedFTU$ReactomeTop %in% names(npgColors))] <- "Other Reactome"
mergedFTU$ReactomeTop <- factor(mergedFTU$ReactomeTop)

allCats <- table(mergedFTU$ReactomeTop)
allCats

```

Compare pathways identified by the two human fluoxetine studies, plus, overlaps with the duloxetine study.

```{r}

percentSignif <- data.frame(Category = names(allCats),
  Fluoxetine = as.numeric(table(mergedFTU$ReactomeTop[mergedFTU$padj.breitfeldFLX < 0.05 & mergedFTU$padj.torresFLX < 0.05]) / allCats * 100),
 Both = as.numeric(table(mergedFTU$ReactomeTop[mergedFTU$padj.breitfeldFLX < 0.05 & mergedFTU$padj.torresFLX < 0.05 &
                                                 mergedFTU$padj.fioriDLX < 0.05]) / allCats * 100)) %>%
  arrange(desc(Fluoxetine))

percentSignif <- filter(percentSignif, Fluoxetine > 1)
percentSignif$Category <- factor(percentSignif$Category, levels = rev(percentSignif$Category))

# Don't double-count "both"
percentSignif$Fluoxetine <- percentSignif$Fluoxetine - percentSignif$Both

percentSignif <- percentSignif %>% pivot_longer(-Category, names_to = "Treatment", values_to = "Percent")
percentSignif$Treatment <- factor(percentSignif$Treatment, levels = c("Fluoxetine", "Both"))
levels(percentSignif$Treatment)[2] <- "Fluoxetine & Duloxetine"

ggplot(percentSignif, aes(x = Percent, y = Category, fill = Treatment)) +
  geom_col(position = "stack", color = "black", linewidth = 1) +
  theme_classic() +
  theme(legend.position = c(0.7, 0.3)) +
  scale_fill_manual(values = c("#A1DBFF", "#DBE866")) +
  ylab("") + xlab("% of Pathways Enriched with q < 0.05")
ggsave("../Figures/ComparisonFigures/FTU_Human_Studies_Summary.tiff", height = 4, width = 5)

```




Look @ agreement

```{r}

mergedSub <- mergedFTU[mergedFTU$padj.breitfeldFLX < 0.05 & mergedFTU$padj.torresFLX < 0.05 &
                                                 mergedFTU$padj.fioriDLX < 0.05,]
nes <- mergedSub[,c(6,13,20)]
table(rowSums(nes > 0))

```

Compare w/ meta-analysis results. 

```{r}

mergeVenn <- list(AllFTU=datA$Pathway[datA$Fish < 0.05 & !is.na(datA$Fish)],
                  SFTU=datS$Pathway[datS$Fish < 0.05 & !is.na(datS$Fish)],
                  Breitfeld=mergedFTU$pathway[mergedFTU$padj.breitfeldFLX < 0.05 & !is.na(mergedFTU$padj.breitfeldFLX)],
                   Torres=mergedFTU$pathway[mergedFTU$padj.torresFLX < 0.05 & !is.na(mergedFTU$padj.torresFLX)],
                   Duloxetine=mergedFTU$pathway[mergedFTU$padj.fioriDLX < 0.05 & !is.na(mergedFTU$padj.fioriDLX)])

venn.diagram(mergeVenn,
             euler.d = TRUE, scaled=TRUE, 
             category=c("Meta-Analysis (All)", "Meta-Analysis (Stressed)", "Breitfeld et al.\n(Fluoxetine)", "Torres et al.\n(Fluoxetine)","Belzeaux et al.\n(Duloxetine)"),
             lty=rep("solid", 5), 
             fill=c(alpha("#21B0FE",0.4), alpha("#2172fe",0.4), alpha("#bf5747",0.4), alpha("#ffca4e",0.4),alpha("#fc8c78",0.4)), 
             col=c("#21B0FE", "#2172fe", "#bf5747", "#ffca4e","#fc8c78"),
             cat.col=c("#21B0FE", "#2172fe", "#bf5747", "#ffca4e","#fc8c78"),
             cex=2, 
             cat.cex=2,
             cat.dist=rep(0.12,5),
             #cat.pos=c(200,160,0),
             margin=0.1,
             disable.logging=TRUE,
             filename = "../Figures/ComparisonFigures/FTU_Fisher_Additional_Studies.tiff")


mergeVenn <- list(AllFTU=datA$Pathway[datA$Max < 0.05 & !is.na(datA$Max)],
                  SFTU=datS$Pathway[datS$Max < 0.05 & !is.na(datS$Max)],
                  Breitfeld=mergedFTU$pathway[mergedFTU$padj.breitfeldFLX < 0.05 & !is.na(mergedFTU$padj.breitfeldFLX)],
                   Torres=mergedFTU$pathway[mergedFTU$padj.torresFLX < 0.05 & !is.na(mergedFTU$padj.torresFLX)],
                   Duloxetine=mergedFTU$pathway[mergedFTU$padj.fioriDLX < 0.05 & !is.na(mergedFTU$padj.fioriDLX)])

venn.diagram(mergeVenn,
             euler.d = TRUE, scaled=TRUE, 
             category=c("Meta-Analysis (All)", "Meta-Analysis (Stressed)", "Breitfeld et al.\n(Fluoxetine)", "Torres et al.\n(Fluoxetine)","Belzeaux et al.\n(Duloxetine)"),
             lty=rep("solid", 5), 
             fill=c(alpha("#FED700",0.4), alpha("#FEE900",0.4), alpha("#bf5747",0.4), alpha("#ffca4e",0.4),alpha("#fc8c78",0.4)), 
             col=c("#FED700", "#FEE900", "#bf5747", "#ffca4e","#fc8c78"),
             cat.col=c("#FED700", "#FEE900", "#bf5747", "#ffca4e","#fc8c78"),
             cex=2, 
             cat.cex=2,
             cat.dist=rep(0.12,5),
             #cat.pos=c(200,160,0),
             margin=0.1,
             disable.logging=TRUE,
             filename = "../Figures/ComparisonFigures/FTU_MaxP_Additional_Studies.tiff")



```

The 5-way venns are pretty messy, try with Stressed only.

```{r}

mergeVenn <- list(SFTU=datS$Pathway[datS$Fish < 0.05 & !is.na(datS$Fish)],
                  Breitfeld=mergedFTU$pathway[mergedFTU$padj.breitfeldFLX < 0.05 & !is.na(mergedFTU$padj.breitfeldFLX)],
                   Torres=mergedFTU$pathway[mergedFTU$padj.torresFLX < 0.05 & !is.na(mergedFTU$padj.torresFLX)],
                   Duloxetine=mergedFTU$pathway[mergedFTU$padj.fioriDLX < 0.05 & !is.na(mergedFTU$padj.fioriDLX)])

venn.diagram(mergeVenn,
             euler.d = TRUE, scaled=TRUE, 
             category=c("Meta-Analysis\n(Fisher)", "Breitfeld et al.\n(Fluoxetine)", "Torres et al.\n(Fluoxetine)","Belzeaux et al.\n(Duloxetine)"),
             lty=rep("solid", 4), 
             fill=c(alpha("#21B0FE",0.4), alpha("#bf5747",0.4), alpha("#ffca4e",0.4),alpha("#fc8c78",0.4)), 
             col=c("#21B0FE", "#bf5747", "#ffca4e","#fc8c78"),
             cat.col=c("#21B0FE", "#bf5747", "#ffca4e","#fc8c78"),
             cex=2, 
             cat.cex=1.9,
             cat.dist=c(0.25, 0.25, 0.16, 0.16),
             cat.pos=c(310,50,340,20),
             margin=0.22,
             disable.logging=TRUE,
             filename = "../Figures/ComparisonFigures/SFTU_Fisher_Additional_Studies.tiff")


mergeVenn <- list(SFTU=datS$Pathway[datS$Max < 0.05 & !is.na(datS$Max)],
                  Breitfeld=mergedFTU$pathway[mergedFTU$padj.breitfeldFLX < 0.05 & !is.na(mergedFTU$padj.breitfeldFLX)],
                   Torres=mergedFTU$pathway[mergedFTU$padj.torresFLX < 0.05 & !is.na(mergedFTU$padj.torresFLX)],
                   Duloxetine=mergedFTU$pathway[mergedFTU$padj.fioriDLX < 0.05 & !is.na(mergedFTU$padj.fioriDLX)])

venn.diagram(mergeVenn,
             euler.d = TRUE, scaled=TRUE, 
             category=c("Meta-Analysis\n(Max-P)", "Breitfeld et al.\n(Fluoxetine)", "Torres et al.\n(Fluoxetine)","Belzeaux et al.\n(Duloxetine)"),
             lty=rep("solid", 4), 
             fill=c(alpha("#FED700",0.4), alpha("#bf5747",0.4), alpha("#ffca4e",0.4),alpha("#fc8c78",0.4)), 
             col=c("#FED700", "#bf5747", "#ffca4e","#fc8c78"),
             cat.col=c("#FED700", "#bf5747", "#ffca4e","#fc8c78"),
             cex=2, 
             cat.cex=1.9,
             cat.dist=c(0.25, 0.25, 0.16, 0.16),
             cat.pos=c(310,50,340,20),
             margin=0.22,
             disable.logging=TRUE,
             filename = "../Figures/ComparisonFigures/SFTU_MaxP_Additional_Studies.tiff")


mergeVenn <- list(Fisher=datS$Pathway[datS$Fish < 0.05 & !is.na(datS$Fish)],
                  MaxP=datS$Pathway[datS$Max < 0.05 & !is.na(datS$Max)],
                   Duloxetine=mergedFTU$pathway[mergedFTU$padj.fioriDLX < 0.05 & !is.na(mergedFTU$padj.fioriDLX)])

venn.diagram(mergeVenn,
             euler.d = TRUE, scaled=TRUE, 
             category=c("Meta-Analysis\n(Fisher)", "Meta-Analysis\n(Max-P)", "Belzeaux et al.\n(Duloxetine)"),
             lty=rep("solid", 3), 
             fill=c(alpha("#21B0FE",0.4), alpha("#FED700",0.4), alpha("#fc8c78",0.4)), 
             col=c("#21B0FE", "#FED700", "#fc8c78"),
             cat.col=c("#21B0FE", "#FED700","#fc8c78"),
             cex=2, 
             cat.cex=2,
             cat.dist=c(0.13,0.025,0.15),
             cat.pos=c(200,160,0),
             margin=0.1,
             disable.logging=TRUE,
             filename = "../Figures/ComparisonFigures/SFTU_Belzeaux_vsMeta.tiff")


```

```{r}

# Identify pathways in common w/ Max-P
mergedSFTU <- merge(datS, mergedFTU, by.x = "Pathway", by.y = "pathway", all = TRUE)
mergedSFTU$Signif <- ifelse(mergedSFTU$Max < 0.05 & mergedSFTU$padj.fioriDLX < 0.05 & 
                  !is.na(mergedSFTU$Max) & !is.na(mergedSFTU$padj.fioriDLX),
                  yes = "Signif", no = "n.s.")
mergedSignif <- mergedSFTU[mergedSFTU$Max < 0.05 & mergedSFTU$padj.fioriDLX < 0.05 & 
                  !is.na(mergedSFTU$Max) & !is.na(mergedSFTU$padj.fioriDLX),]

table(Vote=mergedSignif$Vote > 0,
      Dlx = mergedSignif$NES.fioriDLX > 0)

mergedLabel <- mergedSignif[mergedSignif$Vote %in% c(-6, -5, -4, 4) | grepl("FCGR", mergedSignif$Pathway),]
# Shorten pathway names for labels

mergedLabel$Pathway <- c(#"Epstein-Barr virus infection",
                         "FCGR dependent phagocytosis",
                         "Formation of free 40S subunits",
                         #"Membrane Trafficking",
                         "NMD independent of the EJC",
                         "S Phase",
                         "Signal Transduction",
                         "Signaling by Rho GTPases",
                         "Valine/Leucine/Isoleucine\ndegradation",
                         "Vesicle-mediated transport")


# Plot Vote vs. NES
ggplot(mergedSFTU, aes(x = Vote, y = NES.fioriDLX)) +
  geom_jitter(aes(alpha = Signif, color = Signif), height=0, width = 0.15) +
  geom_hline(yintercept = 0, linetype="dashed") +
  geom_vline(xintercept = 0, linetype="dashed") +
  scale_color_manual(values = c("grey70", "red")) +
  ggrepel::geom_text_repel(data=mergedLabel,
                            aes(label = Pathway), hjust = 0) +
  xlab("Expression Change Agreement\nAcross Fluoxetine Studies (Vote)") +
  ylab("Normalized Enrichement Score (NES)\nfor Duloxetine Treatment vs. Control") +
  theme_classic() +
  guides(color = "none", alpha = "none")
ggsave("../Figures/ComparisonFigures/Belzeaux_vs_SFTUmetaanalysis.tiff",height = 5,width = 6)


```

Remake the summary barplot using Meta-analysis vs. Duloxetine
```{r}

mergedSFTU$ReactomeID <- reactome_hs$ID[match(gsub(" \\|.*", "", mergedSFTU$Pathway), reactome_hs$Name)]
mergedSFTU$ReactomeTop <- reactome_hs$top_level_name[match(mergedSFTU$ReactomeID, reactome_hs$ID)]
mergedSFTU$ReactomeTop[substr(mergedSFTU$Pathway, nchar(mergedSFTU$Pathway)-3, nchar(mergedSFTU$Pathway)) == "KEGG"] <- "KEGG Database"
mergedSFTU$ReactomeTop[!(mergedSFTU$ReactomeTop %in% names(npgColors))] <- "Other Reactome"
mergedSFTU$ReactomeTop <- factor(mergedSFTU$ReactomeTop)

allCats <- table(mergedSFTU$ReactomeTop)
allCats

percentSignif <- data.frame(Category = names(allCats),
  Fluoxetine = as.numeric(table(mergedSFTU$ReactomeTop[mergedSFTU$Max < 0.05]) / allCats * 100),
 Both = as.numeric(table(mergedSFTU$ReactomeTop[mergedSFTU$Max < 0.05 &
                                                 mergedSFTU$padj.fioriDLX < 0.05]) / allCats * 100)) %>%
  arrange(desc(Fluoxetine))

percentSignif <- filter(percentSignif, Fluoxetine > 1)
percentSignif$Category <- factor(percentSignif$Category, levels = rev(percentSignif$Category))

# Don't double-count "both"
percentSignif$Fluoxetine <- percentSignif$Fluoxetine - percentSignif$Both

percentSignif <- percentSignif %>% pivot_longer(-Category, names_to = "Treatment", values_to = "Percent")
percentSignif$Treatment <- factor(percentSignif$Treatment, levels = c("Fluoxetine", "Both"))
levels(percentSignif$Treatment)[2] <- "Fluoxetine & Duloxetine"

ggplot(percentSignif, aes(x = Percent, y = Category, fill = Treatment)) +
  geom_col(position = "stack", color = "black", linewidth = 1) +
  theme_classic() +
  theme(legend.position = c(0.7, 0.3)) +
  scale_fill_manual(values = c("#A1DBFF", "#DBE866")) +
  ylab("") + xlab("% of Pathways Enriched with q < 0.05")
ggsave("../Figures/ComparisonFigures/SFTU_vs_Belzeaux_Summary.tiff", height = 4, width = 5)

```
