---
title: "Sensitivity Analysis Figures"
author: "Caleb Class"
date: "2024-10-17"
output: html_document
---

Number of pathways identified as statistically significant for the full meta-analysis of treated vs. untreated samples, as well as subset analyses of stressed rodents or depressed patients, and unstressed rodents

```{r}

library(VennDiagram)
library(ggvenn)
library(tidyverse)

gseaFull <- readRDS("../MetaDE RDS/AllFTUgsea.rds")
gseaStress <- readRDS("../MetaDE RDS/AllSFTUgsea.rds")
gseaUnstress <- readRDS("../MetaDE RDS/AllXFTUgsea.rds")

fisherVenn <- list(Full=gseaFull$Pathway[gseaFull$Fish < 0.05],
                   Stress=gseaStress$Pathway[gseaStress$Fish < 0.05],
                   Untress=gseaUnstress$Pathway[gseaUnstress$Fish < 0.05])

maxVenn <- list(Full=gseaFull$Pathway[gseaFull$Max < 0.05],
                   Stress=gseaStress$Pathway[gseaStress$Max < 0.05],
                   Untress=gseaUnstress$Pathway[gseaUnstress$Max < 0.05])

venn.diagram(fisherVenn,
             euler.d = TRUE, scaled=TRUE, 
             category=c("Full Set","Stressed Only","Unstressed Only"),
             lty=rep("solid", 3), 
             cex=2, 
             cat.cex=2,
             cat.dist=c(0.07,0.03,0.07),
             cat.pos=c(200,160,0),
             margin=0.1,
             disable.logging=TRUE,
             filename = "../Figures/SensitivityAnalysis/Fisher_TU_Venn.tiff")


venn.diagram(maxVenn,
             euler.d = TRUE, scaled=TRUE, 
             category=c("Full Set","Stressed Only","Unstressed Only"),
             lty=rep("solid", 3), 
             cex=2, 
             cat.cex=2,
             cat.dist=c(0.07,0.03,0.07),
             cat.pos=c(200,160,0),
             margin=0.1,
             disable.logging=TRUE,
             filename = "../Figures/SensitivityAnalysis/MaxP_TU_Venn.tiff")

```


Sensitivity analysis removing DS19 (profiling of 27 brain regions by Rayan et al.). Gene and pathway-level analyses are presented. Dashed lines indicate q=0.05, diagonal line indicates y=x. Number in each quadrant indicates number of genes or pathways in that quadrant. Results of Fisher’s meta-analysi and Max-P. 


```{r}

geneFull <- readRDS("../MetaDE RDS/RatXFTUDE.rds")
geneSA <- readRDS("../MetaDE RDS/SARatXFTUDE.rds")
pathFull <- readRDS("../MetaDE RDS/AllXFTUgsea.rds")
pathSA <- readRDS("../MetaDE RDS/SAAllXFTUgsea.rds")

geneMerge <- merge(geneFull, geneSA, by="Gene",
                   suffixes = c(".Full", ".SA"))

table(Full = geneMerge$Fish.Full < 0.05,
      SA = geneMerge$Fish.SA < 0.05 )
table(Full = geneMerge$Max.Full < 0.05,
      SA = geneMerge$Max.SA < 0.05 )

pathMerge <- merge(pathFull, pathSA, by="Pathway",
                   suffixes = c(".Full", ".SA"))

table(Full = pathMerge$Fish.Full < 0.05,
      SA = pathMerge$Fish.SA < 0.05 )
table(Full = pathMerge$Max.Full < 0.05,
      SA = pathMerge$Max.SA < 0.05 )


```

Gene-level, rat only:

```{r}

ggplot(geneMerge, aes(x=-log10(Fish.Full), y=-log10(Fish.SA))) +
  geom_point(alpha = 0.2, color = "navy") +
  geom_hline(yintercept = -log10(0.05), linetype="dashed") +
  geom_vline(xintercept = -log10(0.05), linetype="dashed") +
  xlab("Fisher -log10(q), Original") +
  ylab("Fisher -log10(q), GSE194289 Removed") +
  theme_classic() 
ggsave("../Figures/SensitivityAnalysis/Fisher_GeneTU_SAscatter.tiff", height = 4, width = 4.5)


ggplot(geneMerge, aes(x=-log10(Max.Full), y=-log10(Max.SA))) +
  geom_point(alpha = 0.2, color = "navy") +
  geom_hline(yintercept = -log10(0.05), linetype="dashed") +
  geom_vline(xintercept = -log10(0.05), linetype="dashed") +
  xlab("MaxP -log10(q), Original") +
  ylab("MaxP -log10(q), GSE194289 Removed") +
  theme_classic() 
ggsave("../Figures/SensitivityAnalysis/MaxP_GeneTU_SAscatter.tiff", height = 4, width = 4.5)


```


```{r}

ggplot(pathMerge, aes(x=-log10(Fish.Full), y=-log10(Fish.SA))) +
  geom_point(alpha = 0.2, color = "navy") +
  geom_hline(yintercept = -log10(0.05), linetype="dashed") +
  geom_vline(xintercept = -log10(0.05), linetype="dashed") +
  xlab("Fisher -log10(q), Original") +
  ylab("Fisher -log10(q), GSE194289 Removed") +
  theme_classic() 
ggsave("../Figures/SensitivityAnalysis/Fisher_PathTU_SAscatter.tiff", height = 4, width = 4.5)


ggplot(pathMerge, aes(x=-log10(Max.Full), y=-log10(Max.SA))) +
  geom_point(alpha = 0.2, color = "navy") +
  geom_hline(yintercept = -log10(0.05), linetype="dashed") +
  geom_vline(xintercept = -log10(0.05), linetype="dashed") +
  xlab("MaxP -log10(q), Original") +
  ylab("MaxP -log10(q), GSE194289 Removed") +
  theme_classic() 
ggsave("../Figures/SensitivityAnalysis/MaxP_PathTU_SAscatter.tiff", height = 4, width = 4.5)


```