---
title: "Treated/Untreated among response groups"
author: "Caleb Class"
date: "2024-01-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(ggrepel)
```

## Loading Data
This meta-analyses summarize comparisons of Responders (post-treatment) vs. untreated, and Non-responders (post-treatment) vs. untreated. In two of the comparisons it was possible to define pre-treatment samples as responders or non-responders--in those cases we conducted treated vs. untreated within response group. In all other cases, they were compared against the same control group.

```{r}

reactome_hs <- readRDS("../FLX RMD/Reactome_HS_withTopLevel.rds")
npgColors <- readRDS("../npgColors.rds")
npgFill <- readRDS("../npgFill.rds")
source("../FLX RMD/read_cpdb_tab.R")
cpdb <- read_cpdb_tab("../FLX RMD/CPDB_pathways_genes_mouse.tab")
names(cpdb) <- gsub(" \\|.*| \\- Mus.*", "", names(cpdb))


datR <- readRDS("../MetaDE RDS/AllSFRCgsea.rds")
datN <- readRDS("../MetaDE RDS/AllSFNCgsea.rds")

```

## Comparison

Merge by pathway and compare Max-P results.

```{r}

summaries <- merge(datR[,10:15], datN[,10:15], by = "Pathway", suffixes = c(".R", ".N"))
summaries$ReactomeID <- reactome_hs$ID[match(gsub(" \\|.*", "", summaries$Pathway), reactome_hs$Name)]
summaries$ReactomeTop <- reactome_hs$top_level_name[match(summaries$ReactomeID, reactome_hs$ID)]
summaries$ReactomeTop[is.na(summaries$ReactomeTop)] <- "KEGG Database"
summaries$ReactomeTop[!(summaries$ReactomeTop %in% names(npgColors))] <- "Other Reactome"
summaries <- summaries %>% 
  mutate(ReactomeTop = factor(ReactomeTop, levels = names(npgColors)))

ggplot(summaries, aes(x=-log10(Max.R), y = -log10(Max.N), 
                      color = ReactomeTop)) +
  geom_point() +
  scale_color_manual(name="ReactomeTop", values = npgColors) +
  theme_classic() +
  guides(color = guide_legend(title = "Pathway Category")) +
  xlab("-log10(q) | Responders") + ylab("-log10(q) | Non-Responders") +
  geom_vline(xintercept = -log10(0.05), color = "darkred", linetype = "dashed") + 
  geom_hline(yintercept = -log10(0.05), color = "darkred", linetype = "dashed")
ggsave("../Figures/ComparisonFigures/TU_NvsR_pmax.tiff", width = 6, height = 4)


table(R = summaries$Max.R < 0.05, NR = summaries$Max.N < 0.05)

```

Next, we'll compare results by Fisher's method.

```{r}



ggplot(summaries, aes(x=-log10(Fish.R), y = -log10(Fish.N), 
                      color = ReactomeTop)) +
  geom_point() +
  scale_color_manual(name="ReactomeTop", values = npgColors) +
  theme_classic() +
  guides(color = guide_legend(title = "Pathway Category")) +
  xlab("-log10(q) | Responders") + ylab("-log10(q) | Non-Responders") +
  geom_vline(xintercept = -log10(0.05), color = "darkred", linetype = "dashed") + 
  geom_hline(yintercept = -log10(0.05), color = "darkred", linetype = "dashed")
ggsave("../Figures/ComparisonFigures/TU_NvsR_fish.tiff", width = 6, height = 4)

#table(R = summaries$Fish.R < 0.05, NR = summaries$Fish.N < 0.05)

```


Finally, we'll focus on those consistently affected in responders (q < 0.05 by Max-P), but consistently unaffected in non-responders (q >= 0.05 by Fisher's method).


```{r}

summaries.signif <- summaries[summaries$Max.R < 0.05 & summaries$Fish.R < 0.05 & summaries$Fish.N >= 0.05 ,]

summaries.signif <- summaries.signif %>% arrange(Max.R) 
# Stretch this pathway name to 2 lines:
summaries.signif$Pathway[5] <- "Activated PKN1 stimulates transcription of\nAR regulated genes KLK2 and KLK3"
summaries.signif$Pathway <- gsub(" \\|.*", "", summaries.signif$Pathway)
summaries.signif <- summaries.signif %>%
  mutate(Pathway = factor(Pathway, levels = rev(Pathway)),
         ReactomeTop = factor(ReactomeTop, levels = names(npgColors)))



ggplot(summaries.signif, aes(x = -log10(Max.R), y = Pathway)) +
  geom_col(aes(fill = ReactomeTop), color = "black", linewidth = 1) + 
  geom_vline(xintercept = -log10(0.05), linetype = "dashed", linewidth = 1, color = "#DC0000") +
  geom_point(aes(x = -log10(Max.R) + 0.13, color = Vote.R), size = 6, show.legend = FALSE) +
  geom_text(aes(x = -log10(Max.R) + 0.13, y = Pathway, label = Vote.R), size = 4, color = "white", fontface = "bold") +
  scale_color_gradient2(low = "blue",high = "red", mid = "gray30", breaks = c(-5, 0, 3), minor_breaks = -5:5) +
  xlab("-log10(q)") + ylab("") +
#  xlim(0, 8) +
  theme(axis.text.y = element_text(size = 8.5)) +
  npgFill +
  guides(fill = guide_legend(title = "Pathway Category")) +
  theme_classic()

ggsave("../Figures/ComparisonFigures/RTUonly_pmax_bar.tiff", width = 7.5, height = 5)


```
